Using Sorghum as an outgroup to find syntenic regions in Maize: regenerating

### 2017-09-01 SubGenome Analysis.Rmd
Added windows paths for load/source

```{r importSynMapData, include=FALSE}
source("~/git/SubGenomes/R/loadData.R")
source("~/git/SubGenomes/R/cleanData.R")
source("~/git/SubGenomes/R/parseSubgenomes.R")
source("~/git/SubGenomes/R/addGOTerms.R")
source("~/git/SubGenomes/R/parseGOSlim.R")
# source("~/git/SubGenomes/R/createTopGO.R")
source("~/git/SubGenomes/R/parseExpressionData.R")

@@

# source("C:\\Users\\Jesse\\Documents\\git\\SubGenome\\R\\parseSubgenomes.R")
# source("C:\\Users\\Jesse\\Documents\\git\\SubGenome\\R\\addGOTerms.R")
```

>>>>

```{r importSynMapData, include=FALSE}
# source("~/git/SubGenomes/R/loadData.R")
# source("~/git/SubGenomes/R/cleanData.R")
# source("~/git/SubGenomes/R/parseSubgenomes.R")
# source("~/git/SubGenomes/R/addGOTerms.R")
# source("~/git/SubGenomes/R/parseGOSlim.R")
# # source("~/git/SubGenomes/R/createTopGO.R")
# source("~/git/SubGenomes/R/parseExpressionData.R")

@@

source("C:\\Users\\Jesse\\Documents\\git\\SubGenome\\R\\loadData.R")
source("C:\\Users\\Jesse\\Documents\\git\\SubGenome\\R\\cleanData.R")
source("C:\\Users\\Jesse\\Documents\\git\\SubGenome\\R\\parseSubgenomes.R")
source("C:\\Users\\Jesse\\Documents\\git\\SubGenome\\R\\addGOTerms.R")
source("C:\\Users\\Jesse\\Documents\\git\\SubGenome\\R\\parseGOSlim.R")
# source("C:\\Users\\Jesse\\Documents\\git\\SubGenome\\R\\createTopGO.R")
source("C:\\Users\\Jesse\\Documents\\git\\SubGenome\\R\\parseExpressionData.R")
```
